---
title: "Exploratory Data Analysis"
author: "Heber Trujillo"
date: "September 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Up

```{r include=FALSE}
library(dplyr)
library(ggplot2)

```
```{r}

train<-read.csv("C:/DISCO D/Bienvenu/Voitures/Individuel/PT/Hackathon/Prework/Mandatory/Data/train.csv")
```
## One Way Analysis

### MSSubClass: Identifies the type of dwelling involved in the sale

```{r}

MSSubClass<-train%>%
  group_by(MSSubClass)%>%
  summarise(count=n(),Avg_SalePrice=mean(SalePrice))


p <- ggplot(data=MSSubClass, aes(x =MSSubClass,y=Avg_SalePrice/500, group=1, label=round(Avg_SalePrice/500,digits = 2))) + 
  geom_col(aes(y = count),fill = "#FFCC00")
p<-p+geom_line( linetype="dashed", size=1,colour ="#0066CC",aes(y=Avg_SalePrice/500))
p <- p + scale_y_continuous(sec.axis = sec_axis(~.*(500), name = "Average Price"))
p <- p + labs(y = "# Observations",
              x = "MSSubClass")
p
```

Seems to There is a clear difference in the average sales price among the MSSubClass's levels


### MSZoning: Identifies the general zoning classification of the sale.

```{r}
MSZoning<-train%>%
  group_by(MSZoning)%>%
  summarise(count=n(),Avg_SalePrice=mean(SalePrice))


p_1 <- ggplot(data=MSZoning, aes(x =MSZoning,y=Avg_SalePrice/500, group=1, label=round(Avg_SalePrice/500,digits = 2))) + 
  geom_col(aes(y = count),fill = "#FFCC00")+ geom_line( linetype="dashed", size=1,colour ="#0066CC",aes(y=Avg_SalePrice/500)) + scale_y_continuous(sec.axis = sec_axis(~.*(500), name = "Average Price")) + labs(y = "# Observations",
              x = "MSZoning")
p_1

```

### LotFrontage: Linear feet of street connected to property

```{r}
p_2 <- ggplot(train, aes(LotFrontage, SalePrice)) + geom_point()+geom_smooth(method = "lm", formula = y ~ splines::bs(x, 3))
p_2

```

  There is a trend for until 100, will be worthy to test it as an explanatory variable. 

### LotArea: Lot size in square feet

```{r}


p_3 <- ggplot(train, aes(LotArea, SalePrice)) + geom_point()+geom_smooth(method = "lm", formula = y ~ splines::bs(x, 3))
p_3

```

Very interesting trend to test


### LandContour: Flatness of the property

```{r}


LandContour<-train%>%
  group_by(LandContour)%>%
  summarise(count=n(),Avg_SalePrice=mean(SalePrice))


p_4 <- ggplot(data=LandContour, aes(x =LandContour,y=Avg_SalePrice/500, group=1, label=round(Avg_SalePrice/500,digits = 2))) + 
  geom_col(aes(y = count),fill = "#FFCC00")+ geom_line( linetype="dashed", size=1,colour ="#0066CC",aes(y=Avg_SalePrice/500)) + scale_y_continuous(sec.axis = sec_axis(~.*(500), name = "Average Price")) + labs(y = "# Observations",
              x = "LandContour")
p_4



```




