---
title: "Model Fitting"
author: "Heber Trujillo"
date: "September 14, 2017"
output: html_document
---
## Set - Up

```{r include=FALSE}
library(gbm)
library(axaml)
library(ggplot2)
library(dplyr)
setwd("C:/DISCO D/Bienvenu/Voitures/Individuel/PT/Hackathon/Prework/Mandatory/Data")
```

```{r}
train<-read.csv("C:/DISCO D/Bienvenu/Voitures/Individuel/PT/Hackathon/Prework/Mandatory/Data/train.csv")
test<-read.csv("C:/DISCO D/Bienvenu/Voitures/Individuel/PT/Hackathon/Prework/Mandatory/Data/test.csv")

```

## Fitting


```{r}

param <- c(481, 10, 0.01)
select<-names(train)
select<-select[2:80]

response<-train$SalePrice

model<-gbm(response~.,data=train[,select], n.trees = param[1], interaction.depth = param[2], shrinkage = param[3],verbose=T)


```


## Goodness of Fit


```{r}


GBM_train<-predict(model,train, n.trees=param[1], type = "response")
train<-data.frame(train,GBM_train)


GBM_test<-predict(model,test, n.trees=param[1], type = "response")
test<-data.frame(test,GBM_test)

kpi_gini(train$GBM_train, truerisk =train$SalePrice)
kpi_gini(test$GBM_test, truerisk =test$SalePrice)

```

Since the overfitting is a very common problem during the fitting process, I have performed the Gini test in order to discard that problem. Here both, train and test have practically the same Gini coefficient.

## Alalysis

```{r, include=FALSE}

factors<-cbind(summary(model)[1],summary(model)[2])
factors<-factors[1:5,]

```

In order to figure out which factors are more relevant predicting the sales price, we are going to use the *summary* function over the model
```{r}

p<-ggplot(data=factors, aes(x=reorder(var,rel.inf), y=rel.inf)) +
  geom_bar(stat="identity",fill = "blue")+ coord_flip()+xlab(label="Factors")+ylab(label="Relative Influence")
p


```

The top 5 factors that make a difference in sales price are:

1. OverallQual:Overall material and finish quality,
2. GrLivArea:Above grade (ground) living area square feet,
3. Neighborhood:Physical locations within Ames city limits,
4. TotalBsmtSF:Total square feet of basement area,
5. BsmtFinSF1:Type 1 finished square feet.

Next, I would like to see the interaction impact between OverallQual and Neighborhood 

```{r}

plot.gbm(model,i.var = c("OverallQual","Neighborhood"),type="response")

```


As I expected, all neighborhoods have the same trend.

## Expor Predictions

```{r}

submission<-test%>%
  select(Id,GBM_test)

submission<-rename(submission,SalePrice=GBM_test)

write.csv(submission,"C:/DISCO D/Bienvenu/Voitures/Individuel/PT/Hackathon/Prework/Mandatory/Data/submission_HTU.CSV",row.names = FALSE)

```
